Forecasting the 2024 Election: Trump Dominates the South, Harris Leads in the Midwest

### 2024-10-22 paper/paper.qmd
committing text changes to paper.qmd

# Visualizing the RMSE and accuracy in a plot with skinnier bars
ggplot(accuracy_rmse_df, aes(x = Metric, y = Value)) +
  geom_bar(stat = "identity", fill = "steelblue", width = 0.2) +  # Adjusted width for skinnier bars
  labs(y = "Value") +
  theme_light()
```
### Confusion Matrix
[@tbl-confusion-matrix] displays the model's predictive performance in distinguishing between state-level wins for Trump (coded as 1) and Harris (coded as 0). In this case, the model correctly predicted 12 Harris wins and 15 Trump wins (true positives and true negatives). However, there were 5 instances where the model incorrectly predicted a Trump win when Harris won (false positives), and 3 instances where it predicted a Harris win when Trump won (false negatives). This breakdown helps assess not only the overall accuracy but also how well the model distinguishes between close contests in different states, which is critical for predicting the outcome of the 2024 presidential election.

>>>>

# Visualizing the RMSE and accuracy in a plot with skinnier bars
ggplot(accuracy_rmse_df, aes(x = Metric, y = Value)) +
  geom_bar(stat = "identity", fill = "steelblue", width = 0.2) +  # Adjusted width for skinnier bars
  labs(y = "Value") +
  theme_light()
```
\newpage

### Confusion Matrix

[@tbl-confusion-matrix] displays the model's predictive performance in distinguishing between state-level wins for Trump (coded as 1) and Harris (coded as 0). In this case, the model correctly predicted 12 Harris wins and 15 Trump wins (true positives and true negatives). However, there were 5 instances where the model incorrectly predicted a Trump win when Harris won (false positives), and 3 instances where it predicted a Harris win when Trump won (false negatives). This breakdown helps assess not only the overall accuracy but also how well the model distinguishes between close contests in different states, which is critical for predicting the outcome of the 2024 presidential election.
